%-------------------------
% Resume in Latex
% Author : Léo Gaudin
% Based off of: https://github.com/jakegut/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Léo Gaudin} \\ \vspace{1pt}
    \href{mailto:leo@gaudin.it}{\underline{leo@gaudin.it}} $|$
    \href{https://linkedin.com/in/leo-gaudin}{\underline{linkedin.com/in/leo-gaudin}} $|$
    \href{https://github.com/leogaudin}{\underline{github.com/leogaudin}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {42}{Málaga, Spain}
      {Degree in Computer Science}{Feb. 2023 -- Jul. 2024}
    \resumeSubheading
      {The University of Western Australia}{Perth, Australia}
      {Bachelor of Arts in Communication and Media Studies}{Feb. 2020 -- Dec. 2022}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Consultant in Software Engineering}{Washington, United States of America (Remote)}
      {The World Bank}{Mar. 2023 -- Present}
      \resumeItemListStart
        \resumeItem{Creator, technical director and sole maintainer of the open-source Track-and-Trace system}
        \resumeItem{Deploy in Senegal, Nigeria, Malawi, Rwanda, Mauritania, and Sierra Leone}
        \resumeItem{Make relevant use of the data collected to provide a good insight into large-scale distributions}
        \resumeItem{Develop a robust ecosystem capable of handling large volumes of parcels (over 300k per account)}
        \resumeItem{Provide flexibility to adapt to any country and their existing processes and structures}
        \resumeItem{Ensure full scanner/GPS functionality on large samples of obsolete devices, in low-coverage zones of Africa}
      \resumeItemListEnd

    \resumeSubheading
      {CTO}{Utrecht, Netherlands (Remote)}
      {BlueTree Group}{Mar. 2023 -- Present}
      \resumeItemListStart
        \resumeItem{Discuss closely with international aid institutions: USAID, FCDO, Mott MacDonald, Expertise France}
        \resumeItem{Work in Rwanda with the government to implement our solutions and train local teams}
        \resumeItem{Deploy routing algorithms to optimize national deliveries in Malawi → 30\% reduction in movements}
      \resumeItemListEnd

    \resumeSubheading
      {IT Consultant}{Utrecht, Netherlands (Remote)}
      {BlueTree Group}{Sep. 2021 -- Mar. 2023}
      \resumeItemListStart
        \resumeItem{Handle the backend of websites}
        \resumeItem{Automate internal processes (distribution lists bulk operations, etc.)}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{La Bacarda} $|$ \emph{React, MongoDB, Express, TypeScript, Stripe, AWS}}{\emph{Apr. 2024 -- Present}}
          \resumeItemListStart
            \resumeItem{Develop a full-stack web application to manage a boat rental company}
            \resumeItem{Aim to digitalize processes, such as booking, payment, and customer management}
            \resumeItem{Implement a payment system using Stripe}
            \resumeItem{Create separate dashboards for clients, employees and boat owners}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Track-and-Trace} $|$ \emph{React, React Native, MongoDB, Express, Vercel}}{\emph{Mar. 2023 -- Present}}
          \resumeItemListStart
            \resumeItem{Create the entire system based on the Bank's requirements, and later the local governments'}
            \resumeItem{Develop and ecosystem of applications: web dashboard, mobile app, and API/DB}
            \resumeItem{Overcome scaling issues to handle large volumes with the very limited Vercel's free tier}
          \resumeItemListEnd
    \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: C, C++, Rust, JavaScript, TypeScript, Python, SQL, PHP} \\
     \textbf{Frameworks}{: React, Express} \\
     \textbf{Tools}{: Git, Docker, Vercel, MongoDB, AWS} \\
    %  \textbf{Libraries}{: pandas, NumPy, Matplotlib}
    }}
 \end{itemize}

%-----------PROGRAMMING SKILLS-----------
\section{Other}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
      \textbf{Languages}{: French (\emph{native}), English (\emph{fluent}), Spanish (\emph{fluent})} \\
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
